---
title: "Lecture notes"
---

+ Chapter 1: Introduction to the Design of Experimental and Observational Studies
  + Motivations
  + Types of Scientific Studies
  + Basic Terminology
  + Most Common Designs of Scientific Studies
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```
  
+ Chapter 2: Single-Factor Studies
  + Single-Factor ANOVA Model
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Analysis of Variance 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + F Test for Equality of Factor Level Means 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Analysis of Factor Level Means 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_4.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Planning of Sample Size
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 2_5.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

+ Chapter 3: ANOVA Diagnostics and Remedial Measures
  + ANOVA Model Assumptions
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Check assumptions 
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

` + Remedies and concerns about assumption violations
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 3_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```
 

+ Chapter 4: Two-Factor Studies with Equal Sample Sizes
  + Two-Way ANOVA Model
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Analysis of Variance
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Tests for Interaction effects and main effects
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Analysis of Factor A and B Main Effects (When Factors Do Not Interact)
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_4.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Analysis of Treatment Means When Interactions Are Present
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 4_5.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  
+ Chapter 5: Two-Factor Studies with One Case Per Treatment
  + Two-Way ANOVA Model without Interaction
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Analysis of Variance
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Test for Factor A and B Main Effects
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Multiple Comparison Procedures
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_4.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Tukey's test
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_5.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Randomized Complete Block Designs
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 5_6.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

+ Chapter 6: Linear Regression Approach to ANOVA
  + Regression Formulation to Single-Factor Studies
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 6_1.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```

  + Linear Regression Formulation to Two-Factor Studies
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 6_2.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```
  
  + Analysis of Covariance Model (ANOCOVA)
```{r, echo=FALSE, out.width = '800px', out.height = '400px', results='asis'}
cat('<embed src="./Lecture notes/Chapter 6_3.pdf" 
    type="application/pdf" 
    width="100%" height="400px" />')
```
  